Supplementary Material

### 2019-12-08 papers/ACL2020/supplementary.tex
[ACL2020] adds supplementary.tex

\title{How to Name a Real-World Object, and how not to}

@@

\begin{document}
\maketitle
\begin{abstract}

\end{abstract}

\section{Introduction}
\label{sec:intro}
\input{introduction}

\section{Related Work}
\label{sec:related}
\input{related}

\section{ManyNames: A Source for Entry-Level Names}
\label{sec:manynames}
\cs{to add: footnote saying that the \mn data will be published upon acceptance of the paper.}
\input{manynames}

\section{Predicting entry-level names}
\label{sec:experiments}
\input{experiments}

\section{Analysis of model naming behavior}
\label{sec:analysis}
\input{analysis}

\section{Conclusions}
\label{sec:conclusions}

%\bibliography{BLA}
%\bibliographystyle{acl_natbib}

%\appendix
%
% \section{Appendices}
% \label{sec:appendix}
% \iffalse
% Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper.
% Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
% Upon acceptance, the appendices come after the references, as shown here.

% \paragraph{\LaTeX-specific details:}
% Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
% \fi

% \section{Supplemental Material}
% \label{sec:supplemental}
% \iffalse
% Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
% Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
% \fi

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "acl2020_main"
%%% End:

>>>>

\title{Supplementary Material}

@@

\begin{document}

\section{Verification Procedure with AMT}
\label{sec:verif}
\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{images/verification-interface.pdf}
	\caption{A screenshot of our verification task interface. Up to ten names could be shown for an image in this way (the number of available colors in the second task would increase accordingly).}
	\label{fig:verification-interface}
\end{figure*}

\cs{The text is is just copied from the main, it needs to be adapted here.}
We provided (and clarified by means of explanation and visual examples) the following definition: \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
When the participant selected slightly or totally inadequate, four additional icons would appear to indicate the type of inadequacy: ``linguistic mistake'', ``named object not tightly in bounding box'', ``named object mistaken for something it's not'', and ``something else''.
We provided detailed instructions and examples at the top, as well as informative hover texts on all the buttons.

@@
